Probability

### 2016-04-22 prob.tex
prob.tex \subsection{Plan} fix a typo...
prob.tex \subsection{HIlbert Space with Finite Set-Valued Probability Measure} updated...

\documentclass{article}
\usepackage{fullpage}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{array}
\usepackage{mathrsfs}
\usepackage[all]{xy}

@@

In the remainder of the paper, we consider variations of quantum
probability spaces motivated by computation of numerical quantities in
a world with limited resources:
\begin{itemize}
\item Instead of the Hilbert space $\Hilb$ (constructed over the
  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
  consider variants constructed over finite
  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
\item Instead of real-valued probability measures producing results in
  the uncountable and uncomputable interval $[0,1]$, we will consider
  finite set-valued probablitity measures~\cite{Artstein1972,PuriRalescu1983}.
\end{itemize}
We will then ask if it is possible to construct variants of quantum
probability spaces under these conditions. The main question is
related to the definition of probability measures: is it possible to
still define a probability measure as a function that depends on a
single state? Specifically,
\begin{itemize}
\item given a state $\ket{\psi}$, is there a probability measure
  mapping events to probabilities that only depends on $\ket{\psi}$?
  In the conventional quantum probability space, the answer is yes by
  the Born rule~\cite{Born1984,Mermin2007} and the map is given by:
  $E \mapsto \ip{\psi}{E\psi}$.
\item given a probability measure $\mu$
  mapping each event $E$
  to a probability, is there is a \emph{unique} state $\psi$
  such that $\mu(E)
  =
  \ip{\psi}{E\psi}$. In the conventional case, the answer is yes by
  Gleason's
  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
\end{itemize}

@@

>>>>

\documentclass{article}
\usepackage{fullpage}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{array}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{amsmath}

@@

In the remainder of the paper, we consider variations of quantum
probability spaces motivated by computation of numerical quantities in
a world with limited resources:
\begin{itemize}
\item Instead of the Hilbert space $\Hilb$ (constructed over the
  uncountable and uncomputable complex numbers $\mathbb{C}$), we will
  consider variants constructed over finite
  fields~\cite{HansonOrtizSabryEtAl2015,DQT2014,geometry2013}.
\item Instead of real-valued probability measures producing results in
  the uncountable and uncomputable interval $[0,1]$, we will consider
  finite set-valued probablitity measures~\cite{Artstein1972,PuriRalescu1983}.
\end{itemize}
We will then ask if it is possible to construct variants of quantum
probability spaces under these conditions. The main question is
related to the definition of probability measures: is it possible to
still define a probability measure as a function that depends on a
single state? Specifically,
\begin{itemize}
\item given a state $\ket{\psi}$, is there a probability measure
  mapping events to probabilities that only depends on $\ket{\psi}$?
  In the conventional quantum probability space, the answer is yes by
  the Born rule~\cite{Born1984,Mermin2007} and the map is given by:
  $E \mapsto \ip{\psi}{E\psi}$.
\item given a probability measure $\mu$
  mapping each event $E$
  to a probability, is there a \emph{unique} state $\psi$
  such that $\mu(E)
  =
  \ip{\psi}{E\psi}$. In the conventional case, the answer is yes by
  Gleason's
  theorem~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
\end{itemize}

@@

In order to simplify the discussion, we will focus on $\mathscr{L}_{2}=\left\{ \textrm{impossible},\textrm{possible}\right\} $
where impossible and possible means $\left\{ 0\right\} $ and $\left(0,1\right]$
respectively while our result can be easily extend to other values
with the form $\left\{ \left\{ 0\right\} ,\left(0,\frac{1}{n}\right],\ldots,\left(\frac{n-1}{n},1\right]\right\} $.

Because $\mathscr{L}_{2}$ is a partition of $\left[0,1\right]$~\cite{Artin1991,Wechler1992,PurdomBrown1995,DummitFoote2004},
there is a natural surjective map~$\iota:\left[0,1\right]\rightarrow\mathscr{L}_{2}$
defined by $\iota\left(0\right)=\textrm{impossible}$ and $\iota\left(x\right)=\textrm{possible}$
for $x\ne0$. By applying $\iota$, we can define the corresponding
Born rule~$\bar{\mu}$ by $\bar{\mu}_{\psi}(E)=\iota\left(\mu_{\psi}(E)\right)$,
and the corresponding probability measure~$\hat{\mu}$ should satisfy: 
\begin{itemize}
\item $\hat{\mu}(\mathbb{1})=\textrm{possible}$, and 
\item for a collection of pairwise orthogonal $E_{i}$, we have $\hat{\mu}(\sum_{i}E_{i})=\bigvee_{i}\hat{\mu}(E_{i})$,
where $x\vee y=\textrm{impossible}$ if and only if $x=y=\textrm{impossible}$.
\end{itemize}
However, there is a $\mathscr{L}_{2}$-valued probability measure
\[
\hat{\mu}_{1}\left(E\right)=\begin{cases}
\textrm{impossible} & \textrm{, if }E=\proj{+};\\
\bar{\mu}_{0}(E) & \textrm{, otherwise.}
\end{cases}
\]
such that $\hat{\mu}_{1}\ne\bar{\mu}_{\psi}$ for all mixed state
$\ket{\psi}$.
